CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2021-01-07 codecheck-paper.tex
about to make edits after talking to Daniel

\begin{itemize}
\item Check with Giuliano re: ``code works''. Write to Naomi.
\item Use "execution" insteand of "sharing" in title?
\item Can we introduce "research compendium" as a term?
\item Should we make code and data sharing a prerequisite or leave that door open?
\item Take a look at the Lancet's statistical review process (areas for improvement by authors) \url{https://www.thelancet.com/journals/lancet/article/PII0140-6736(92)90409-V/fulltext}
\item How to relate to "reproducibility does not matter but trust does", see \url{https://gmbecker.github.io/MayInstituteKeynote2019/outline.html}
\item Should we ask the people currently listed in the acknowledgements?
\item revisit \url{https://github.com/codecheckers/discussion}
\item \url{https://hdsr.mitpress.mit.edu/pub/f0obb31j/release/1} and other articles form the HDSR special issue
\end{itemize}

@@

Specific to the field of Mathematics, the RCR was also  expected to apply a
review of the software itself if the system it runs on cannot be evaluated by
an independent party.
The TOMS RCR also notes the importance of communication and expects
collaboration between author and RCR reviewers.
The TOMS creators share thoughts around reviewer selection and also put trust
in reviewer judgement over numerical bit-wise perfection.
A key difference is that authors opt-in with an \emph{RCR Review Request} and
the RCR reports, which are very similar to CODECHECK certificates, are
published in the TOMS journal next to the actual papers.
A search on Crossref\footnote{\url{https://search.crossref.org/?q=\%22Replicated+Computations+Results+\%28RCR\%29+Report\%22&from_ui=yes&page=2}; search executed
on 2020-12-10} shows 15 RCR Reports to be published and the workflow to be 
extended to the ACM journal \emph{Transactions on Modeling and Computer 
Simulation (TOMACS)}\footnote{\url{https://dl.acm.org/journal/tomacs/author-guidelines#rcrini}}.

>>>>

\begin{enumerate}
\item Check with Giuliano re: ``code works''. Write to Naomi.
\item Use "execution" insteand of "sharing" in title?
\item Can we introduce "research compendium" as a term?
\item Should we make code and data sharing a prerequisite or leave that door open?
\item Take a look at the Lancet's statistical review process (areas for improvement by authors) \url{https://www.thelancet.com/journals/lancet/article/PII0140-6736(92)90409-V/fulltext}
\item How to relate to "reproducibility does not matter but trust does", see \url{https://gmbecker.github.io/MayInstituteKeynote2019/outline.html}
\item Should we ask the people currently listed in the acknowledgements?
\item revisit \url{https://github.com/codecheckers/discussion}
\item \url{https://hdsr.mitpress.mit.edu/pub/f0obb31j/release/1} and other articles form the HDSR special issue
\item \url{https://av.tib.eu/media/42484} > "Code will make systematic mistakes, not random mistakes", "code is more reliable (and auditable) than a human"
\end{enumerate}

@@

Specific to the field of Mathematics, the RCR was also  expected to apply a
review of the software itself if the system it runs on cannot be evaluated by
an independent party.
The TOMS RCR also notes the importance of communication and expects
collaboration between author and RCR reviewers.
The TOMS creators share thoughts around reviewer selection and also put trust
in reviewer judgement over numerical bit-wise perfection.
A key difference is that authors opt-in with an \emph{RCR Review Request} and
the RCR reports, which are very similar to CODECHECK certificates, are
published in the TOMS journal next to the actual papers.
A search on Crossref\footnote{\url{https://search.crossref.org/?q=\%22Replicated+Computations+Results+\%28RCR\%29+Report\%22&from_ui=yes&page=2}; search executed
on 2020-12-10} shows 15 RCR Reports to be published and the workflow to be 
extended to the ACM journal \emph{Transactions on Modeling and Computer 
  Simulation (TOMACS)}
%% SJE TODO - fix footnote
%% \footnote{\url{https://dl.acm.org/journal/tomacs/author-guidelines-%35-rcrini}}.
